---
title: "Gacha Pull Simulation Results"
output:
  pdf_document:
    toc: true
  html_document:
    theme: cosmo
    toc: true
encoding: "UTF-8"
---

```{r setup, include=FALSE}
library(ggplot2)
library(knitr)
library(dplyr)
library(kableExtra)
library(tidyr)
library(viridis)
library(viridisLite)
knitr::opts_chunk$set(echo = FALSE)

# Source utility scripts
source("R/load_data.R")
source("R/stats_utils.R")
source("R/plotting.R")
```

## Loading and Preparing Data

```{r load_data}
# Load all game data
data_list <- load_game_data()

# Prepare combined data for comparative analysis
all_results <- prepare_combined_data(data_list)
```

## Basic Statistics

```{r calculate_stats}
# Calculate basic statistics for each game
stats_hsr <- calculate_basic_stats(data_list$hsr)
stats_genshin <- calculate_basic_stats(data_list$genshin)
stats_zzz <- calculate_basic_stats(data_list$zzz)
stats_arknights <- calculate_basic_stats(data_list$arknights)
stats_wuwa <- calculate_basic_stats(data_list$wuwa)

# Create a summary table of basic statistics
basic_stats <- bind_rows(
  mutate(stats_hsr, Game = "HSR"),
  mutate(stats_genshin, Game = "Genshin"),
  mutate(stats_zzz, Game = "ZZZ"),
  mutate(stats_arknights, Game = "Arknights"),
  mutate(stats_wuwa, Game = "Wuwa")
)
```

```{r success_rates}
# Calculate success rates for all games
success_rates <- calculate_success_rates(data_list)

# Prepare data for plotting success rates
success_rates_hoyo <- success_rates$hoyo %>%
  pivot_longer(cols = c(Limited_Rate, Weapon_Rate, Four_Star_Rate, Three_Star_Rate),
               names_to = "Type", values_to = "Rate")

success_rates_arknights <- success_rates$arknights %>%
  pivot_longer(cols = c(Six_Star_Rate, Five_Star_Rate, Four_Star_Rate, Three_Star_Rate),
               names_to = "Type", values_to = "Rate")

success_rates_wuwa <- success_rates$wuwa %>%
  pivot_longer(cols = c(Five_Star_Rate, Four_Star_Rate, Limited_Four_Rate, Three_Star_Rate),
               names_to = "Type", values_to = "Rate")

# Combine for overall comparison
success_rates_long <- bind_rows(
  success_rates_hoyo,
  success_rates_arknights,
  success_rates_wuwa
)
```

```{r cumulative_probabilities}
# Calculate cumulative probabilities for all games
cum_data <- prepare_cumulative_data(data_list)
```

## Pull Distribution Comparison

This section compares the distribution of pulls required to get the desired items across different games.

```{r pull_distributions}
# Plot pull density distributions
plot_pull_density(all_results)

# Plot pull boxplots
plot_pull_boxplots(all_results)
```

## Success Rates Visualization

The following charts show the success rates for different rarities across the games.

```{r success_rates_plot}
# Plot success rates
plot_success_rates(success_rates_long)
```

## Cumulative Probability Analysis

This analysis shows the probability of obtaining the desired item within a certain number of pulls.

```{r cumulative_analysis}
# Plot cumulative probabilities
plot_cumulative_probabilities(cum_data)
```

## Character vs Weapon Banner Analysis

For HoYo games (HSR, Genshin Impact, ZZZ), we can compare the character and weapon banners.

```{r banner_comparison}
# Prepare data for banner comparison
hoyo_games <- bind_rows(
  data_list$hsr,
  data_list$genshin,
  data_list$zzz
)

# Plot banner comparison
plot_banner_comparison(hoyo_games)
```

## Game-Specific Statistics

### Honkai: Star Rail

```{r hsr_stats}
# Plot HSR histogram
plot_game_histogram(data_list$hsr, "HSR", game_colors["HSR"])

# Calculate and display detailed HSR statistics
hsr_detailed <- calculate_detailed_stats(data_list$hsr)

kable(head(hsr_detailed, 10),
      digits = 4,
      caption = "HSR Pull Statistics (First 10 rows)",
      format = "html") %>%
    kable_styling(bootstrap_options = c("striped", "hover"))
```

### Genshin Impact

```{r genshin_stats}
# Plot Genshin histogram
plot_game_histogram(data_list$genshin, "Genshin Impact", game_colors["Genshin"])

# Calculate and display detailed Genshin statistics
genshin_detailed <- calculate_detailed_stats(data_list$genshin)

kable(head(genshin_detailed, 10),
      digits = 4,
      caption = "Genshin Pull Statistics (First 10 rows)",
      format = "html") %>%
    kable_styling(bootstrap_options = c("striped", "hover"))
```

### ZZZ

```{r zzz_stats}
# Plot ZZZ histogram
plot_game_histogram(data_list$zzz, "ZZZ", game_colors["ZZZ"])

# Calculate and display detailed ZZZ statistics
zzz_detailed <- calculate_detailed_stats(data_list$zzz)

kable(head(zzz_detailed, 10),
      digits = 4,
      caption = "ZZZ Pull Statistics (First 10 rows)",
      format = "html") %>%
    kable_styling(bootstrap_options = c("striped", "hover"))
```

### Arknights

```{r arknights_stats}
# Plot Arknights histogram
plot_game_histogram(data_list$arknights, "Arknights", game_colors["Arknights"])

# Calculate and display detailed Arknights statistics
arknights_detailed <- calculate_detailed_stats(data_list$arknights)

kable(head(arknights_detailed, 10),
      digits = 4,
      caption = "Arknights Pull Statistics (First 10 rows)",
      format = "html") %>%
    kable_styling(bootstrap_options = c("striped", "hover"))
```

### Wuwa

```{r wuwa_stats}
# Plot Wuwa histogram
plot_game_histogram(data_list$wuwa, "Wuwa", game_colors["Wuwa"])

# Calculate and display detailed Wuwa statistics
wuwa_detailed <- calculate_detailed_stats(data_list$wuwa)

kable(head(wuwa_detailed, 10),
      digits = 4,
      caption = "Wuwa Pull Statistics (First 10 rows)",
      format = "html") %>%
    kable_styling(bootstrap_options = c("striped", "hover"))
```

## Summary and Conclusions

This analysis provides insights into the gatcha mechanics of five different games:

1. **Honkai: Star Rail** - Characterized by [describe key findings]
2. **Genshin Impact** - Shows [describe key findings]
3. **ZZZ** - Demonstrates [describe key findings]
4. **Arknights** - Features [describe key findings]
5. **Wuwa** - Distinguished by [describe key findings]

Overall, we can see that [general conclusions about the differences between the games' gatcha systems].
